### 2016-09-07 notions.tex
comments on the comments

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?} \tsnote{Email discussion. At this point,
I'm happy just making~$S$ part of the experiment ``name'', the
way~$\distr{}{}$ is now.  The distribution seems not to matter for
correctness, at least for the schemes we consdier.} \jnote{If instead we choose $S$ from ${\cal D}$, then
is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
yes, if for no other reason than to allow~$A$ to know when it asking
a pointless query.  But also it will make no difference to the
provable correctness of the constructions we consider.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.}
\tsnote{I don't see how this correctness notion is specialized to
  set-multiplicity data structures.  I don't think we actually
  specialize notions in any way until, maybe, the OW privacy notion.
  It is true that we only deliver concrete results for set-multiplicty
data structures, however.}\jnote{Why does $A$ output
anything at all?}\tsnote{To signify it is finished execution.  Matter
of taste, I'm not hardover about it.}

@@

\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
and in the general case I think the former is what we
want.}\tsnote{This may have implications for the efficiency of
reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
counter and returned this was to avoid~$A$ be forced to evalutate
queries of unknown computational cost.} 
%\jnote{I also changedthe definition so the adversary has to find $r$
% {\bf unique} inputs on which there is an error.}

@@

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon$.
\jnote{Note~$q$ is overloaded here.}\tsnote{True, and do we even need
  it, other than for making a compact statements of comparison with
  NY?  Why not just have explict advantage bounding statements, as we
  do for our other results, relating our notion to NY's?  (And,
  probably, moving all of that to an appendix, as you later suggest.)}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

@@

\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
is ``better'' than the definition in
Figure~\ref{fig:NYcorrectness}?}\tsnote{I don't know, but we do seem
to have a compelling list of shortcomings of their notion, which ours
doesn't seem to suffer. Anyway, it's a bit of an unfair comparison, in
their favor.  You're lifting their notion to ours, which is more
general.  And by the time we get to that, we have already done them
the favor of cleaning up the syntax, so that their ``lifted'' notion
looks better than it was.}

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq
1$.
\tsnote{this could easily be written, albeit less compactly, without
introducing the resource-parameterized notation; likewise the others.}
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon)$-NY-correct,
and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
some $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon/r$.
(Note that
we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
With probability at least
$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon/r)=\epsilon$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

@@

\jnote{I'm not sure what to conclude from any of the results above. The proofs
are also all trivial.} \tsnote{Trivial or not, it's all part of the
overall contribution, which is putting this topic on a solid
foundation.  We can move it all to an appendix, but I still see it as
very worthwhile.}

@@

\newcommand{\leak}{{\sf leak}}
\subsection{Privacy}
\jnote{Define appropriate notion of min-entropy for our setting.
Define one-wayness.}

@@

One can also consider the orthogonal notion of \emph{privacy} for a
data structure. \jnote{I am still hoping that we can treat data structures
at an even more general level than set-representation data structures.}
We formalize two types of privacy notions. The first captures
a ``one-wayness'' property that (informally) requires that
the representation of some set~$S$ does not make it any easier for an attacker
to learn an element of~$S$.
The second definition
captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
not leak any information about the set~$S$ they represent beyond
what is captured in some explicit leakage function.

\jnote{OK, from here on I specialize to set-representation data
  structures\ldots} \tsnote{I don't understand this comment.  That's
  what our syntax supports anyway, so how is this specializing?}

>>>>

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?} \tsnote{Email discussion. At this point,
I'm happy just making~$S$ part of the experiment ``name'', the
way~$\distr{}{}$ is now.  The distribution seems not to matter for
correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
yes, if for no other reason than to allow~$A$ to know when it asking
a pointless query.  But also it will make no difference to the
provable correctness of the constructions we consider.}
\jnote{OK, I think I would just change the definitions so that the attacker
chooses $S$.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.}
\tsnote{I don't see how this correctness notion is specialized to
  set-multiplicity data structures.  I don't think we actually
  specialize notions in any way until, maybe, the OW privacy notion.
  It is true that we only deliver concrete results for set-multiplicty
data structures, however.}

@@

\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
and in the general case I think the former is what we
want.}\tsnote{This may have implications for the efficiency of
reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
counter and returned this was to avoid~$A$ be forced to evaluate
queries of unknown computational cost.} \jnote{Not sure what you mean. If the
oracle returns $q(S)$ then $A$ doesn't have to evaluate it. All $A$ has to do
is an equality check to see if $a=q(S)$ or not.}

@@

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon$.
\jnote{Note~$q$ is overloaded here.}\tsnote{True, and do we even need
  it, other than for making a compact statements of comparison with
  NY?  Why not just have explicit advantage bounding statements, as we
  do for our other results, relating our notion to NY's?  (And,
  probably, moving all of that to an appendix, as you later suggest.)}
\jnote{Not sure what you mean. I was pointing out that we use $q$ both for a particular
query, as well as for the bound on the number of attacker's queries. Don't we want to
keep track of the query bound?}

@@

\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
is ``better'' than the definition in
Figure~\ref{fig:NYcorrectness}?}\tsnote{I don't know, but we do seem
to have a compelling list of shortcomings of their notion, which ours
doesn't seem to suffer. Anyway, it's a bit of an unfair comparison, in
their favor.  You're lifting their notion to ours, which is more
general.  And by the time we get to that, we have already done them
the favor of cleaning up the syntax, so that their ``lifted'' notion
looks better than it was.} \jnote{I agree, it's just that once we have ``lifted'' it
appropriately, it's not clear what's wrong with it and why we introduce a different
style of definition.}

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq
1$.
\tsnote{this could easily be written, albeit less compactly, without
introducing the resource-parameterized notation; likewise the others.} \jnote{How?}
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon)$-NY-correct,
and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
some $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon/r$.
(Note that
we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
With probability at least
$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon/r)=\epsilon$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

@@

\jnote{I'm not sure what to conclude from any of the results above. The proofs
are also all trivial.} \tsnote{Trivial or not, it's all part of the
overall contribution, which is putting this topic on a solid
foundation.  We can move it all to an appendix, but I still see it as
very worthwhile.} \jnote{It's worth having for completeness, I'm just not sure
what we (or the reader) is supposed to do with it. It's not like we can draw
any simple conclusions like ``our definition implies theirs'' or anything.}

@@

\newcommand{\leak}{{\sf leak}}
\subsection{Privacy}

@@

One can also consider the orthogonal notion of \emph{privacy} for a
data structure.
We formalize two types of privacy notions. The first captures
a ``one-wayness'' property that (informally) requires that
the representation of some set~$S$ does not make it any easier for an attacker
to learn an element of~$S$.
The second definition
captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
not leak any information about the set~$S$ they represent beyond
what is captured in some explicit leakage function.

### 2016-09-07 syntax.tex
beginning to address JK's comments in notions.tex
comments on the comments

The classical Bloom filter is a special case of a set-multiplicity
data structure, as set-membership query is a type of
set-multiplicity query.  Specifically, 
%\jnote{Only handles sets, not multisets.} 
let $\Gamma=\bits$, and fix functions
$k(\cdot)$ and $m(\cdot)$ parameterizing the scheme. Algorithm
$\Rep$, on input a set~$S$, computes $k=k(|S|)$ and $m=m(|S|)$ and
then chooses $k$ functions $h_1, \ldots, h_k \in \mathcal{H}$ for
some function family $\mathcal{H}=\{h \colon \univ \to
\{1,2,\ldots,m\}\}$. \jnote{Note depends on $m$. It might be easier
(especially since we talk about error) to already let the hash
functions be independent random oracles.} \tsnote{I don't see the
problem.  $\Rep$ knows~$m$, so any function (whose range admits at
least~$m$ values) can be effectively treated as having range~$[m]$.
But I added a sentence at the end of this paragraph, too.  See if that
helps.} 
It then computes an $m$-bit array~$M$ (initialized to 0 everywhere) by setting
$M[h_i(x)]=1$ for all $i\in [k]$ and $x \in S$.  Finally, $\Rep$
returns $\privaux=\emptystring$ and $\pubaux = \langle M,h_1,h_2,\ldots,h_k\rangle$ as the
representation.
%
Algorithm~$\Qry$ is defined so that, on input
$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that the standard Bloom filter
analysis treats $h_1,h_2,\ldots,h_k$ as independent random functions,
which we may capture in the ROM with some simple adjustments to the above.

@@

By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture
the so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{xxx}. \jnote{Details have to be filled in.} This stores
xor-shares of bitstring~$x \in S$ at positions
$h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores
a hash $g(x)$ at positions determined by
$h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
\todo{Check the correctness of this claim.}

>>>>

The classical Bloom filter is a special case of a set-multiplicity
data structure, as set-membership queries are a type of
set-multiplicity query.  Specifically,
%\jnote{Only handles sets, not multisets.}
let $\Gamma=\bits$, and fix functions $k(\cdot)$ and $m(\cdot)$
parameterizing the scheme. Algorithm $\Rep$, on input a set~$S$,
computes $k=k(|S|)$ and $m=m(|S|)$ and then chooses $k$ functions
$h_1, \ldots, h_k \in \mathcal{H}$ for some function family
$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$. \jnote{Note
depends on $m$. It might be easier (especially since we talk about
error) to already let the hash functions be independent random
oracles.} \tsnote{I don't see the problem.  $\Rep$ knows~$m$, so any
function (whose range admits at least~$m$ values) can be effectively
treated as having range~$[m]$. But I added a sentence at the end of
this paragraph, too.  See if that helps.} \jnote{$\Rep$ knows $m$,
but $m$ can take any value so we need an $\mathcal{H}$ that is
defined for every possible~$m$.} It then computes an $m$-bit
array~$M$ (initialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
$\privaux=\emptystring$ and $\pubaux = \langle
M,h_1,h_2,\ldots,h_k\rangle$ as the representation.
%
Algorithm~$\Qry$ is defined so that, on input
$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that the standard Bloom filter
analysis treats $h_1,h_2,\ldots,h_k$ as independent random functions,
which we may capture in the ROM with some simple adjustments to the above.

@@

By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture
the so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{xxx}. \todo{Details have to be filled in.} This stores
xor-shares of bitstring~$x \in S$ at positions
$h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores
a hash $g(x)$ at positions determined by
$h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
\todo{Check the correctness of this claim.}
